A Mechanised Library for Generic (Co)Programming

### 2024-03-18 paper/paper.tex
stuff

\section{Related Work}

\begin{itemize}
  \item McBride devised a generalisation of Bove and Capretta's general
recursive function monad~\cite{McBride15, BoveC01}
  \item Guarded recursion for productive definitions and general recursion
~\cite{AtkeyM13, PaviottiMB15}
  \item PACO library~\cite{HurNDV13}
  \item Sized Types \cite{HughesPS96, abs-1202-3496}
  \item Copatterns \cite{AbelPTS13, AbelP16}
  \item IMPORTANT!!!!! Coq extraction from recursion
    schemes~\cite{larchey2022braga} \dcas{Check bibtex}
  \item Not that related: extraction for mutable arrays~\cite{SAKAGUCHI2020102372}
  \item Recursion schemes in Coq (but not hylos)~\cite{MurataE19}
  \item EVEN MORE IMPORTANT!!! 2023 POPL paper on divide and conquer code in
    Coq~\cite{AbreuDHJMS23}.  Some differences to point out: they require
    functional-extensionality axiom. We are axiom-free. Little discussion about
    extraction. They focus mostly on erasing termination proofs, but they do
    not discuss "what does their extracted code look like". Their
    representation of Functors leads me to think that they will produce loads
        of "Obj.magic", but we'd need to check this. \mvol{We have a story for this now: obj.magic harms interaction with other ocaml code, the resulting ocaml code is not natural to read, and in general more complex/strange extracted code is likely to be less efficient and harder to optimise.}
        \item Extraction of Distributed Mobile code in Coq~\cite{MiculanP12}.
\end{itemize}

@@

Within the domain of program optimization, program calculation serves as a
well-established programming technique aimed at deriving efficient programs
from their naive counterparts through systematic program transformation. This
area has been extensively explored over the years. Tesson et al.\ demonstrated
the efficacy of leveraging Coq to establish an approach for implementing a
robust system dedicated to verifying the correctness of program transformations
for functions that manipulate lists~\cite{10.1007/978-3-642-17796-5_10}. Murata
and Emoto went further and\ldots~\cite{MurataE19}

\mvol{Need more general citations for program calculation.}

>>>>

\section{Related Work}
%
%\begin{itemize}
%  \item McBride devised a generalisation of Bove and Capretta's general
%recursive function monad~\cite{McBride15, BoveC01}
%  \item Guarded recursion for productive definitions and general recursion
%~\cite{AtkeyM13, PaviottiMB15}
%  \item PACO library~\cite{HurNDV13}
%  \item Sized Types \cite{HughesPS96, abs-1202-3496}
%  \item Copatterns \cite{AbelPTS13, AbelP16}
%  \item Not that related: extraction for mutable arrays~\cite{SAKAGUCHI2020102372}
%        \item Extraction of Distributed Mobile code in Coq~\cite{MiculanP12}.
%\end{itemize}

@@

Within the domain of program optimization, program calculation serves as a
well-established programming technique aimed at deriving efficient programs
from their naive counterparts through systematic program
transformation~\cite{gibbonsSquiggol}. This area has been extensively explored
over the years. Tesson et al.\ demonstrated the efficacy of leveraging Coq to
establish an approach for implementing a robust system dedicated to verifying
the correctness of program transformations for functions that manipulate
lists~\cite{10.1007/978-3-642-17796-5_10}. Murata and Emoto went further and
formalised recursion schemes in Coq~\cite{MurataE19}. Their development does
not include hylomorphisms and dynamorphisms, and relies on the functional
extensionality axiom, as well as further extensionality axioms for each
coinductive datatype that they use. They do not discuss the extracted OCaml
code from their formalisation.  Larchey-Wendling and Monin encode recursion
schemes in Coq, by formalising computational graphs of
algorithms~\cite{larchey2022braga}. Their work does not focus on encoding
generic recursion schemes, and proving their algebraic laws.  Castro et
al.~\cite{farmsCastro} encode the laws of hylomorphisms as part of the type
system of a functional language to calculate parallel programs from
specifications. Their work focuses on parallelism, and they do not formalise
their approach in a proof assistant, and the laws of hylomorphisms are axioms
in their system.

%\mvol{Need more general citations for program calculation.}
